---
title: "Interactive Charts in R"
author: 'Por: Eduardo Q Marques'
date: "Abril de 2020"
output: 
  html_document:
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plotly)
library(gapminder)
```


Hi guys!

It's really amazing what you can do within the R environment and one of the main desires of those who work with R is to make beautiful graphics.
I speak for myself!
For that, ggplot2 is an essential package for those who like to make beautiful graphics. But did you know that you can do more? Yes! You can create an interactive chart with any ggplot chart using the plotly package.
Want to learn how to do?
Then come with me!

### Load packages and data frame
First, let's start loading the necessary packages. We will use the gapminder package to obtain a database for our class.

```{r packges}
library(ggplot2)
library(plotly)
library(gapminder)
```

Now let's create our dataframe and visualize it.

```{r dataframe}
df <- gapminder
df
```

These Gapminder data are about life expectancy, GDP per capita and population by country, comprising several years.
To facilitate our visualization in the graph, we will filter only the year 1992.

```{r filter}
df = df%>%
  filter(year==1992)
df
```

### Plotting the data
Now our data is ready to be plotted. Let's create a beautiful dot plot in ggplot using data from GDP per capita, life expectancy, population and continent.

```{r ggplot}
ggplot(df, aes(gdpPercap, lifeExp, size = pop, color=continent)) +
  geom_point() +
  theme_bw()
```

### Interactive Charts
Ok ... the graph was beautiful, but so what? How to make it interactive?

This is the easiest part of all! We will simply put the graph we created inside an object and load it using the ggplotly function.

```{r interactive}
gg = ggplot(df, aes(gdpPercap, lifeExp, size = pop, color=continent)) +
  geom_point() +
  theme_bw()

ggplotly(gg)
```

Of course, there are many more functions and possibilities using the plotly package. To learn more read the package documentation and visit the plotly website (https://plotly.com/).

Make good use of this information!


